Knowledge Representation for Service Robots: Supply and Demand

### 2012-05-14 krs-survey.tex
Completed section on theory of mind + fixed sally ann figure

\usepackage{hyperref}
\usepackage{graphicx}

@@

The idea of a \emph{theory of mind}~\cite{Premack1978} emerges from the
perspective taking ability. It can be defined as the ability for one to
understand and acknowledge that other intelligent agents can have their own
mental state (that includes beliefs, intents, desires, knowledge) that is
possibly different from one's own.

\begin{figure}
        \centering
        \includegraphics[width=0.9\columnwidth]{sally_ann.pdf}
        \caption{The standard ``Sally and Ann'' false-beliefs experiment, taken from~\cite{Leslie2000}.}
        \label{fig|sally-ann}
\end{figure}

Perceiving and understanding other's \emph{attention} has been identified as
essential to the development of a theory of mind by
Baron-Cohen~\cite{Baron-Cohen1985, Leslie2000}. In
robotics~\cite{Scassellati2002}

>>>>

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{subfigure}

@@

The idea of a \emph{theory of mind}~\cite{Premack1978} emerges from the
perspective taking ability. It can be defined as the ability for one to
understand and acknowledge that other intelligent agents can have their own
mental state (that includes beliefs, intents, desires, knowledge) that is
possibly different from one's own. The \emph{attention} plays a central to the
development and recognition of a theory of mind~\cite{Baron-Cohen1985,
Leslie2000}.

A notable consequence of having a theory of mind is the representation of
\emph{false beliefs}, \ie, facts that are believed to be true for an agent, but
false for other ones. The ``Sally and Ann'' experiment
(figure~\ref{fig|sally-ann}) is a classical example of a false belief
situation. In~\ref{fig|sally-ann-final}, Sally thinks the ball is in the beige
box because she did not see Ann moving it. An external observer asked ``Where
will Sally look for the ball?'' would answer ``in the blue box'' without a
theory of mind (\ie, a model of the knowledge of Sally), whereas it would
correctly answer ``In the beige box'' with a theory of mind.

\begin{figure}
        \centering
        \subfigure[Sally puts the ball in the beige box.]{
            \includegraphics[scale=0.3]{sally_ann1.pdf}
        } \hspace{8pt} %
        \subfigure[She goes away.]{
            \includegraphics[scale=0.3]{sally_ann2.pdf}
        } \\
        \subfigure[Ann moves the ball.]{
            \includegraphics[scale=0.3]{sally_ann3.pdf}
        } \hspace{8pt} %
        \subfigure[Where will Sally look for the ball?]{
            \includegraphics[scale=0.3]{sally_ann4.pdf}
            \label{fig|sally-ann-final}
        }
        \caption{The standard ``Sally and Ann'' false-beliefs experiment, taken
        from~\cite{Leslie2000}.}

        \label{fig|sally-ann}
\end{figure}

Scassellati~\cite{Scassellati2002} is amongst the researcher having studied
theory of mind for robots.
